\inputencoding{utf8}
\HeaderA{optimsimplex.reflect}{Simplex Reflection}{optimsimplex.reflect}
\keyword{method}{optimsimplex.reflect}
%
\begin{Description}\relax
This function returns a new simplex by reflection of the current simplex with
respect to the first vertex in the simplex. This move is used in the centered
simplex gradient.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
  optimsimplex.reflect(this = NULL, fun = NULL, data = NULL)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{this}] An simplex object.
\item[\code{fun}] The function to compute at vertices. The function is expected to
have the following input and output arguments:

\Tabular{l}{
myfunction <- function(x, this)\{ \\{}
... \\{}
return(list(f=f,this=this)) \\{}
\}
}
where x is a row vector and this a user-defined data, i.e. the \code{data}
argument.
\item[\code{data}] A user-defined data passed to the function. If data is provided,
it is passed to the callback function both as an input and output argument.
\code{data} may be used if the function uses some additionnal parameters. It
is returned as an output parameter because the function may modify the data
while computing the function value. This feature may be used, for example,
to count the number of times that the function has been called.
\end{ldescription}
\end{Arguments}
%
\begin{Value}
Return a list with the following elements: \begin{description}

\item[r] The reflected simplex object.
\item[data] The updated user-defined data.

\end{description}

\end{Value}
%
\begin{Author}\relax
Author of Scilab optimsimplex module: Michael Baudin (INRIA - Digiteo)

Author of R adaptation: Sebastien Bihorel (\email{sb.pmlab@gmail.com})
\end{Author}
%
\begin{SeeAlso}\relax
\code{\LinkA{optimsimplex.new}{optimsimplex.new}}
\end{SeeAlso}
